---
title: "2025 Feedback Email Analyzer"
format: 
  html:
    theme: cosmo
    toc: true
    toc_float: true
    code_folding: show
    css: |
      .main-container {
        max-width: 1200px;
        margin: 0 auto;
        padding: 20px;
      }
      .section-header {
        background: linear-gradient(135deg, #458A73, #94D3BE);
        color: white;
        padding: 15px 20px;
        border-radius: 8px;
        margin: 30px 0 20px 0;
        font-size: 1.5em;
        font-weight: bold;
        box-shadow: 0 4px 6px rgba(0,0,0,0.1);
      }
      .subsection-header {
        background: #94D3BE;
        color: #458A73;
        padding: 10px 15px;
        border-radius: 5px;
        margin: 20px 0 15px 0;
        font-size: 1.2em;
        font-weight: bold;
      }
      .analysis-box {
        background: #f8f9fa;
        border-left: 4px solid #458A73;
        padding: 15px;
        margin: 15px 0;
        border-radius: 0 5px 5px 0;
      }
      .chart-container {
        background: white;
        padding: 20px;
        border-radius: 8px;
        box-shadow: 0 2px 4px rgba(0,0,0,0.1);
        margin: 15px 0;
      }
---

```{r setup}
library(googlesheets4)
library(blastula)
library(tidyverse)
library(scales)
library(ellmer)
library(gt)
library(here)

# Authentication and AI setup
gs4_auth(email = "vicent.boned.11@gmail.com")
chat <- chat_ollama(model = "llama3.1:8b", seed = 123)
```

```{r functions}
# Reusable function for AI analysis
analyze_feedback <- function(data, edition, feedback_column, analysis_type = "feedback") {
  feedback_text <- data %>%
    filter(edition == !!edition, !is.na(!!sym(feedback_column))) %>%
    filter(!!sym(feedback_column) != "") %>%
    select(aux = !!sym(feedback_column)) %>%
    pluck("aux") %>%
    paste0(collapse = " ")
  
  if (analysis_type == "feedback") {
    prompt <- paste0("Summarise the whole feedback in 3 positive points and 3 negative points \n \n", feedback_text)
  } else if (analysis_type == "ideas") {
    prompt <- paste0("Summarise the whole list of ideas in 3 ideas \n \n", feedback_text)
  }
  
  chat$chat(prompt)
}

# Function to create rating comparison chart
create_rating_chart <- function(data, rate_column, title, subtitle = "") {
  data %>% 
    group_by(edition, !!sym(rate_column)) %>% 
    summarise(r = n(), .groups = "drop") %>% 
    ggplot(aes(x = as.character(edition),
               y = r,
               fill = as.factor(!!sym(rate_column)))) +
    geom_col(position = "fill", color = "black") +
    scale_y_continuous(labels = label_percent()) +
    labs(title = title, 
         subtitle = subtitle,
         x = "Edition", 
         y = "Percentage",
         fill = "Rating") +
    theme_minimal() +
    theme(plot.background = element_rect(fill = "#94D3BE"),
          title = element_text(color = "#458A73", face = "bold"),
          panel.grid.major.x = element_blank()) +
    scale_fill_viridis_d()
}

# Function to create classes rating by level chart
create_level_rating_chart <- function(data) {
  data %>% 
    group_by(level, edition) %>% 
    summarise(avg_response = mean(classes_rate, na.rm = TRUE),
              responses = n(), .groups = "drop") %>%
    ggplot(aes(x = level, y = avg_response)) +
    geom_col(fill = "#458A73") +
    coord_flip(ylim = c(3,5)) +
    geom_text(aes(label = label_number(accuracy = .1)(avg_response)), 
              hjust = -1) + 
    geom_text(aes(label = paste0("n: ", responses), y = 3.5)) +
    labs(title = "Average Class Ratings by Level", x = NULL, y = "Average Rating") +
    theme_minimal() +
    facet_wrap(vars(edition)) +
    theme(panel.grid.major.y = element_blank(),
          panel.grid.minor = element_blank(),
          panel.grid.major.x = element_line(colour = "#458A73"),
          plot.background = element_rect(fill = "#94D3BE"),
          title = element_text(color = "#458A73", face = "bold"),
          panel.background = element_rect(fill = "#94D3BE"))
}
```

```{r data-processing}
# Define column names
colnames <- c("timestamp", "name", "participation", "classes_rate", "classes_why", 
              "parties_rate", "parties_why", "worth_money_rate", "worth_money_why", 
              "open_feedback", "future_ideas")

# Load data from Google Sheets
df2025 <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1w6gBzV0NJi6RcpKAMWE7SGR-px_B9Oo6lNQmZywSbuY/edit?gid=1456259706#gid=1456259706") %>%
  mutate(edition = 2025)

df2024 <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1s9dERJcK3UEk9UQdaHYOyVW-SE2_zgwCjUCU79o4mS4/edit?gid=1407248365#gid=1407248365") %>% 
  mutate(edition = 2024)

# Standardize column names
names(df2024) <- c(colnames, "edition")
names(df2025) <- c(colnames, "edition")

# Combine and process data
all_feedback <- df2024 %>% 
  union(df2025) %>%
  mutate(
    lindy_intermediate = str_detect(participation, "Lindy Hop Intermediate(?! / Advanced)"),
    lindy_advanced = str_detect(participation, "Lindy Hop Advanced"),
    lindy_int_adv = str_detect(participation, "Lindy Hop Intermediate / Advanced"),
    solo_jazz = str_detect(participation, "Solo Jazz"),
    balboa_a = str_detect(participation, "Balboa A \\(Advanced\\)"),
    balboa_b = str_detect(participation, "Balboa B \\(Intermediate\\)"),
    blues = str_detect(participation, "Blues")
  )

# Create level-based analysis dataset
all_feedback_by_level <- all_feedback %>% 
  pivot_longer(names_to = "level", values_to = "levelatt", cols = lindy_intermediate:blues) %>% 
  filter(levelatt)
```

# Executive Summary

```{r summary-table}
# Create summary table of average ratings
all_feedback %>% 
  select(edition, classes_rate, parties_rate, worth_money_rate) %>%
  pivot_longer(cols = !edition) %>% 
  group_by(edition, name) %>% 
  summarise(rate = mean(value, na.rm = TRUE), .groups = "drop") %>% 
  pivot_wider(names_from = name, values_from = rate) %>% 
  gt(groupname_col = NULL) %>%
  tab_header(title = "Average Ratings by Edition") %>%
  fmt_number(columns = everything(), decimals = 2)
```

# Classes Analysis {.section-header}

## Classes Rating Comparison

```{r classes-rating-chart}
# Classes rating comparison chart
create_rating_chart(all_feedback, "classes_rate", "Classes Rating Comparison", "Percentage distribution across editions")
```

## Classes Rating by Level

```{r classes-level-chart}
# Classes rating by level
create_level_rating_chart(all_feedback_by_level)
```

## Classes Feedback Analysis

```{r classes-ai-analysis}
# AI analysis of classes feedback
classes_feedback_2024 <- analyze_feedback(all_feedback, 2024, "classes_why")
classes_feedback_2025 <- analyze_feedback(all_feedback, 2025, "classes_why")
```

### 2024 Classes Feedback
<div class="analysis-box">
```{r}
classes_feedback_2024
```
</div>

### 2025 Classes Feedback
<div class="analysis-box">
```{r}
classes_feedback_2025
```
</div>

# Parties Analysis {.section-header}

## Parties Rating Comparison

```{r parties-rating-chart}
# Parties rating comparison chart
create_rating_chart(all_feedback, "parties_rate", "Parties Rating Comparison", "Percentage distribution across editions")
```

## Parties Feedback Analysis

```{r parties-ai-analysis}
# AI analysis of parties feedback
parties_feedback_2024 <- analyze_feedback(all_feedback, 2024, "parties_why")
parties_feedback_2025 <- analyze_feedback(all_feedback, 2025, "parties_why")
```

### 2024 Parties Feedback
<div class="analysis-box">
```{r}
parties_feedback_2024
```
</div>

### 2025 Parties Feedback
<div class="analysis-box">
```{r}
parties_feedback_2025
```
</div>

# Value for Money Analysis {.section-header}

## Worth Money Rating Comparison

```{r worth-money-chart}
# Worth money rating comparison chart
all_feedback %>% 
  group_by(edition, worth_money_rate) %>% 
  summarise(r = n(), .groups = "drop") %>% 
  ggplot(aes(x = as.character(edition),
             y = r,
             fill = worth_money_rate)) +
  geom_col(position = "fill", color = "black") +
  scale_y_continuous(labels = label_percent()) +
  labs(title = "Worth Money Rating Comparison", 
       subtitle = "Percentage distribution across editions",
       x = "Edition", 
       y = "Percentage",
       fill = "Rating") +
  theme_minimal() +
  theme(plot.background = element_rect(fill = "#94D3BE"),
        title = element_text(color = "#458A73", face = "bold")) +
  ggthemes::scale_fill_fivethirtyeight()
```

## Worth Money Feedback Analysis

```{r worth-money-ai-analysis}
# AI analysis of worth money feedback
worth_feedback_2024 <- analyze_feedback(all_feedback, 2024, "worth_money_why")
worth_feedback_2025 <- analyze_feedback(all_feedback, 2025, "worth_money_why")
```

### 2024 Worth Money Feedback
<div class="analysis-box">
```{r}
worth_feedback_2024
```
</div>

### 2025 Worth Money Feedback
<div class="analysis-box">
```{r}
worth_feedback_2025
```
</div>

# Overall Feedback Analysis {.section-header}

## Open Feedback Analysis

```{r overall-feedback-ai-analysis}
# AI analysis of overall feedback
overall_feedback_2024 <- analyze_feedback(all_feedback, 2024, "open_feedback")
overall_feedback_2025 <- analyze_feedback(all_feedback, 2025, "open_feedback")
```

### 2024 Overall Feedback
<div class="analysis-box">
```{r}
overall_feedback_2024
```
</div>

### 2025 Overall Feedback
<div class="analysis-box">
```{r}
overall_feedback_2025
```
</div>

## Future Ideas Analysis

```{r future-ideas-ai-analysis}
# AI analysis of future ideas
future_ideas_2024 <- analyze_feedback(all_feedback, 2024, "future_ideas", "ideas")
future_ideas_2025 <- analyze_feedback(all_feedback, 2025, "future_ideas", "ideas")
```

### 2024 Future Ideas
<div class="analysis-box">
```{r}
future_ideas_2024
```
</div>

### 2025 Future Ideas
<div class="analysis-box">
```{r}
future_ideas_2025
```
</div>

# Comprehensive Comparison {.section-header}

```{r comprehensive-comparison}
# Comprehensive comparison analysis
comparison_analysis <- chat$chat(
  paste0(
    "Based on the following feedback data, provide a comprehensive comparison between 2024 and 2025 editions:\n\n",
    "2024 Classes Feedback: ", classes_feedback_2024, "\n\n",
    "2025 Classes Feedback: ", classes_feedback_2025, "\n\n",
    "2024 Parties Feedback: ", parties_feedback_2024, "\n\n", 
    "2025 Parties Feedback: ", parties_feedback_2025, "\n\n",
    "2024 Worth Money Feedback: ", worth_feedback_2024, "\n\n",
    "2025 Worth Money Feedback: ", worth_feedback_2025, "\n\n",
    "2024 Overall Feedback: ", overall_feedback_2024, "\n\n",
    "2025 Overall Feedback: ", overall_feedback_2025, "\n\n",
    "2024 Future Ideas: ", future_ideas_2024, "\n\n",
    "2025 Future Ideas: ", future_ideas_2025, "\n\n",
    "Please provide:\n",
    "1. What went well in 2024 vs 2025\n",
    "2. What went badly in 2024 vs 2025\n", 
    "3. Key differences and improvements between editions\n",
    "4. Overall recommendations for future editions"
  )
)
```

## Key Findings and Recommendations

<div class="analysis-box">
```{r}
comparison_analysis
```
</div>
