---
title: "MSS 2026 Registration Processing"
format: html
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

rm(list = ls())

source(here::here("R", "config.R"))
source(here::here("R", "helpers.R"))
source(here::here("R", "firestore_api.R"))
fn_setup()

# Fixed timestamp for the entire run — ensures hold-period logic is deterministic
# within a single execution (no drift from Sys.time() called at different points)
RUN_TIMESTAMP <- Sys.time()
cat("Run timestamp:", format(RUN_TIMESTAMP, "%Y-%m-%d %H:%M:%S %Z"), "\n")
```

## Load Registrations from Firebase

```{r}
#| label: load-data

df_raw <- fn_get_registrations(filters = list(pass = c("lindy", "lindy_solo")))
write_sheet(df_raw, ss = GOOGLE_SHEETS$registrations_2026, "raw_data")
```

## Load Previous State (for idempotency & state-diff)

```{r}
#| label: load-previous-state

# Try to read the previous final_tally from Google Sheets.
# This is the source of truth for who was already CONFIRMED / WAITLIST / ON_HOLD.
# If it doesn't exist yet (first run), we start with an empty frame.
prev_tally <- tryCatch(
  read_sheet(GOOGLE_SHEETS$registrations_2026, sheet = "final_tally"),
  error = function(e) {
    message("No previous final_tally found — first run.")
    tibble(
      email        = character(),
      prev_status  = character(),
      prev_lindy_in = logical(),
      prev_solo_in  = logical()
    )
  }
)

# Keep only the columns we need for comparison
if (nrow(prev_tally) > 0 && "status" %in% names(prev_tally)) {
  prev_tally <- prev_tally |>
    select(
      email,
      prev_status   = status,
      prev_lindy_in = any_of("lindy_in"),
      prev_solo_in  = any_of("solo_in")
    ) |>
    mutate(
      # Coalesce logicals to FALSE (not status, which is character)
      across(any_of(c("prev_lindy_in", "prev_solo_in")), ~ coalesce(as.logical(.), FALSE)),
      prev_status = coalesce(prev_status, "UNKNOWN")
    )
} else {
  prev_tally <- tibble(
    email         = character(),
    prev_status   = character(),
    prev_lindy_in = logical(),
    prev_solo_in  = logical()
  )
}

cat("Previous tally rows:", nrow(prev_tally), "\n")
```

## Clean and Prepare Data

```{r}
#| label: clean-data

# Firebase schema columns:
# name, email, pass, role, partner_email, level, created_at, 
# payment_status, amount_cents, id, stripe_* fields

df_clean <- df_raw |>
  filter(!is.na(email) & email != "") |> 
  filter(pass %in% c("lindy","lindy_solo")) %>% 
  mutate(
    created_at = as.POSIXct(created_at),
    name = str_to_title(name),
    email = str_to_lower(email),
    partner_email = str_to_lower(coalesce(partner_email, "")),
    level = str_to_lower(level),
    # Detect which passes they registered for from 'pass' field
    # 2026: Lindy, Lindy + Solo
    lindy = str_detect(pass, regex("lindy", ignore_case = TRUE)),
    solo = str_detect(pass, regex("solo", ignore_case = TRUE)),
    # Standardize partner field (guard against partner_email == own email)
    partner_email = if_else(partner_email == email, "", partner_email),
    has_partner = partner_email != "" & !is.na(partner_email)
  ) |>
  arrange(created_at) %>% 
  # Deduplicate: keep the latest registration per email

  # (handles re-submissions; latest row has the most up-to-date preferences)
  group_by(email) |>
  slice_max(created_at, n = 1, with_ties = FALSE) |>
  ungroup() |>
  select(-c(stripe_payment_method_id)) %>% 
  relocate(created_at, id, email, name, pass, role, level, has_partner, partner_email) %>% 
  arrange(created_at)

# Report duplicates removed
n_before_dedup <- df_raw |> filter(!is.na(email) & email != "", pass %in% c("lindy","lindy_solo")) |> nrow()
cat("Registrations before dedup:", n_before_dedup,
    "| after dedup:", nrow(df_clean),
    "| removed:", n_before_dedup - nrow(df_clean), "duplicates\n")

# Show pass distribution
df_clean |> count(role, level) %>% 
  pivot_wider(names_from = role, values_from = n, values_fill = 0)

write_sheet(df_clean, ss = GOOGLE_SHEETS$registrations_2026, "clean_data")
```

## Define Quotas

```{r}
#| label: quotas

# Quotas derived from the single source of truth in config.R → GROUP_CAPACITIES
LINDY_QUOTAS <- tibble(
  level = c("intermediate", "int-advanced", "advanced"),
  quota = c(
    GROUP_CAPACITIES$intermediate,
    GROUP_CAPACITIES$intermediate_advanced,
    GROUP_CAPACITIES$advanced
  )
)

SOLO_QUOTA <- GROUP_CAPACITIES$solo

# Hold period: days to wait for a listed partner to register before treating as single
PARTNER_HOLD_DAYS <- 3

cat("Lindy quotas:\n")
print(LINDY_QUOTAS)
cat("Solo quota:", SOLO_QUOTA, "\n")
cat("Hold period:", PARTNER_HOLD_DAYS, "days\n")
```

## Helper Functions for Matching

```{r}
#| label: helper-functions

#' Match leaders and followers for a dance track
#' 
#' @param df Data frame with registrations for a specific track
#' @param quota_df Data frame with level and quota columns (or single number for all levels)
#' @param hold_days Number of days to hold a spot for an unmatched partner before
#'   treating the registrant as a single. 0 = no hold (immediate single matching).
#' @param run_ts Fixed timestamp for this run (avoids Sys.time() drift)
#' @param prev_pairs Optional tibble of ALL pairs from the previous run.
#'   Eligible pairs are locked: their members are removed from matching pools
#'   and they receive priority pair_numbers so they can never be pushed out
#'   of the quota by new registrations.
#' @return List with `pairs` (matched pairs with eligibility) and `on_hold`
#'   (registrants still waiting for their partner within the hold period)
fn_match_partners <- function(df, quota_df, hold_days = 0,
                              run_ts = RUN_TIMESTAMP,
                              prev_pairs = NULL) {
  
  # Separate leaders and followers
  leaders <- df |>
    filter(role == "leader") |>
    select(created_at, email, level, has_partner, partner_email)
  
  followers <- df |>
    filter(role == "follower") |>
    select(created_at, email, level, has_partner, partner_email)
  
  # ── Step 0: Lock ALL previously eligible pairs (couples + singles) ──
  # Locked pairs keep their spots unconditionally. Their members are removed
  # from the matching pools so they cannot be re-matched or displaced.
  if (!is.null(prev_pairs) && nrow(prev_pairs) > 0) {
    locked_pairs <- prev_pairs |> filter(eligible)
    locked_emails <- c(
      locked_pairs$email_leader[!is.na(locked_pairs$email_leader)],
      locked_pairs$email_follower[!is.na(locked_pairs$email_follower)]
    )
    # Remove locked people from ALL pools (before couple matching + singles)
    leaders   <- leaders   |> filter(!email %in% locked_emails)
    followers <- followers |> filter(!email %in% locked_emails)
    
    cat("  Locked", nrow(locked_pairs), "previously eligible pairs (",
        sum(locked_pairs$is_couple), "couples,",
        sum(!locked_pairs$is_couple), "singles pairs )\n")
  } else {
    locked_pairs <- NULL
  }
  
  # ── Step 1: Match registered couples (mutual partner reference + same level) ──
  # Only runs on the REMAINING (non-locked) leaders and followers.
  couples <- leaders |>
    filter(has_partner) |>
    inner_join(
      followers |> filter(has_partner),
      by = c("partner_email" = "email", "level" = "level"),
      suffix = c("_leader", "_follower")
    ) |>
    filter(email == partner_email_follower) |>
    select(
      email_leader = email,
      email_follower = partner_email,
      level,
      created_at_leader,
      created_at_follower
    ) |>
    mutate(is_couple = TRUE)
  
  # ── Step 2: Unmatched partners (listed partner didn't register / different level) ──
  unmatched_leaders <- leaders |>
    filter(has_partner) |>
    anti_join(couples, by = c("email" = "email_leader"))
  
  unmatched_followers <- followers |>
    filter(has_partner) |>
    anti_join(couples, by = c("email" = "email_follower"))
  
  # ── Step 2b: Hold period (uses fixed run_ts, NOT Sys.time()) ──
  if (hold_days > 0) {
    hold_cutoff <- run_ts - as.difftime(hold_days, units = "days")
    
    on_hold_leaders   <- unmatched_leaders  |> filter(created_at > hold_cutoff)
    expired_leaders   <- unmatched_leaders  |> filter(created_at <= hold_cutoff)
    on_hold_followers <- unmatched_followers |> filter(created_at > hold_cutoff)
    expired_followers <- unmatched_followers |> filter(created_at <= hold_cutoff)
    
    on_hold <- bind_rows(
      on_hold_leaders   |> mutate(role = "leader"),
      on_hold_followers |> mutate(role = "follower")
    )
  } else {
    expired_leaders   <- unmatched_leaders
    expired_followers <- unmatched_followers
    on_hold <- tibble(
      created_at    = as.POSIXct(character()),
      email         = character(),
      level         = character(),
      has_partner   = logical(),
      partner_email = character(),
      role          = character()
    )
  }
  
  # ── Step 3: Build singles pool (true singles + expired unmatched partners) ──
  single_leaders <- leaders |>
    filter(!has_partner) |>
    bind_rows(expired_leaders |> select(-partner_email)) |>
    arrange(created_at)
  
  single_followers <- followers |>
    filter(!has_partner) |>
    bind_rows(expired_followers |> select(-partner_email)) |>
    arrange(created_at)
  
  # ── Step 3b: Match new singles by index within each level ──
  single_leaders <- single_leaders |>
    group_by(level) |> arrange(created_at) |> mutate(idx = row_number()) |> ungroup()
  single_followers <- single_followers |>
    group_by(level) |> arrange(created_at) |> mutate(idx = row_number()) |> ungroup()
  
  non_couples <- single_leaders |>
    full_join(single_followers, by = c("idx", "level"), suffix = c("_leader", "_follower")) |>
    select(email_leader, email_follower, level, created_at_leader, created_at_follower) |>
    mutate(is_couple = FALSE)
  
  # ── Step 4: Combine new couples + new singles into "new_pairs" ──
  new_pairs <- bind_rows(couples, non_couples) |>
    mutate(
      created_at_pair = pmax(created_at_leader, created_at_follower, na.rm = TRUE),
      is_locked = FALSE
    )
  
  # ── Step 5: Combine locked + new, number with locked pairs first ──
  # Locked pairs get priority pair_numbers (sorted by their original created_at_pair).
  # New pairs are appended after, so they can only fill remaining quota slots.
  if (!is.null(locked_pairs) && nrow(locked_pairs) > 0) {
    locked_for_combine <- locked_pairs |>
      mutate(
        created_at_pair = pmax(created_at_leader, created_at_follower, na.rm = TRUE),
        is_locked = TRUE
      ) |>
      select(email_leader, email_follower, level,
             created_at_leader, created_at_follower,
             is_couple, created_at_pair, is_locked)
    
    all_pairs <- bind_rows(locked_for_combine, new_pairs)
  } else {
    all_pairs <- new_pairs
  }
  
  # Number pairs: locked first (preserving their order), then new by created_at_pair
  all_pairs <- all_pairs |>
    group_by(level) |>
    arrange(!is_locked,
            is.na(email_leader) | is.na(email_follower),
            created_at_pair,
            .by_group = TRUE) |>
    mutate(pair_number = row_number()) |>
    ungroup()
  
  # Apply quotas: locked pairs are ALWAYS eligible; new pairs fill remaining slots
  if (is.data.frame(quota_df)) {
    all_pairs <- all_pairs |>
      left_join(quota_df, by = "level") |>
      mutate(
        eligible = is_locked |
          (pair_number <= quota &
           !is.na(email_leader) & !is.na(email_follower))
      )
  } else {
    all_pairs <- all_pairs |>
      mutate(
        quota = quota_df,
        eligible = is_locked |
          (pair_number <= quota &
           !is.na(email_leader) & !is.na(email_follower))
      )
  }
  
  list(pairs = all_pairs, on_hold = on_hold)
}

#' Convert paired data to individual eligibility
#' 
#' @param pairs_df Data frame with matched pairs
#' @param track_name Name of the track (for column naming)
#' @return Data frame with email and eligibility status
fn_pairs_to_individual <- function(pairs_df, track_name) {
  col_name <- paste0(track_name, "_in")
  
  pairs_df |>
    select(email_leader, email_follower, eligible) |>
    pivot_longer(
      cols = c(email_leader, email_follower),
      names_to = "role",
      values_to = "email"
    ) |>
    filter(!is.na(email)) |>
    # Collapse to one row per email; eligible if ANY pair grants eligibility
    group_by(email) |>
    summarise(!!col_name := any(eligible), .groups = "drop")
}
```

## Process Lindy Hop Registrations

```{r}
#| label: lindy-processing

df_lindy <- df_clean |>
  filter(lindy) |>
  select(created_at, email, role, level, has_partner, partner_email)

# Load ALL previous pairs from Google Sheets (if they exist).
# fn_match_partners handles locking internally (filters eligible pairs itself).
prev_lindy_pairs <- tryCatch(
  read_sheet(GOOGLE_SHEETS$registrations_2026, sheet = "lindy_pairs_locked"),
  error = function(e) {
    message("No previous lindy_pairs_locked sheet — first run.")
    NULL
  }
)

# Match partners for Lindy (passing previous pairs for stability)
lindy_result <- fn_match_partners(
  df_lindy,
  quota_df  = LINDY_QUOTAS,
  hold_days = PARTNER_HOLD_DAYS,
  run_ts    = RUN_TIMESTAMP,
  prev_pairs = prev_lindy_pairs
)
lindy_pairs   <- lindy_result$pairs
lindy_on_hold <- lindy_result$on_hold

# Summary by level
lindy_summary <- lindy_pairs |>
  group_by(level) |>
  summarise(
    complete_pairs = sum(!is.na(email_leader) & !is.na(email_follower)),
    eligible_pairs = sum(eligible, na.rm = TRUE),
    quota = first(quota),
    .groups = "drop"
  )

print(lindy_summary)

# Get individual eligibility
lindy_eligible <- fn_pairs_to_individual(lindy_pairs, "lindy")

# ── Monotonic safety net: never demote a previously confirmed lindy participant ──
# Even if pair-locking covers most cases, this guarantees lindy_in can only go
# from FALSE → TRUE, never TRUE → FALSE across re-runs.
if (nrow(prev_tally) > 0) {
  lindy_before <- lindy_eligible  # snapshot before overlay
  lindy_eligible <- lindy_eligible |>
    left_join(prev_tally |> select(email, prev_lindy_in), by = "email") |>
    mutate(lindy_in = coalesce(lindy_in, FALSE) | coalesce(prev_lindy_in, FALSE)) |>
    select(email, lindy_in)
  
  # Count people who would have been demoted without this safety net
  n_saved <- sum(lindy_eligible$lindy_in & !coalesce(lindy_before$lindy_in, FALSE))
  if (n_saved > 0) {
    cat("  ⚠ Monotonic safety net saved", n_saved, "lindy participants from demotion\n")
  }
}

# Persist locked-in pairs for next run (source of truth for stability)
write_sheet(lindy_pairs, ss = GOOGLE_SHEETS$registrations_2026, sheet = "lindy_pairs_locked")
```

## Process Solo Jazz Registrations

```{r}
#| label: solo-processing

# Solo doesn't require partner matching, just queue-entry order.
# Eligibility depends on being accepted in Lindy (if registered for both).
#
# Queue ordering: a person joins the Solo queue at the moment they become
# Lindy-eligible, NOT at the moment they registered. This prevents someone
# who registered early but was on the Lindy waitlist from displacing a person
# who has been confirmed for Solo since an earlier run.
#
# Tier 0 – not registered for Lindy at all (eligible from registration)
# Tier 1 – already Lindy-confirmed in the previous run (eligible since then)
# Tier 2 – newly Lindy-confirmed this run (join end of queue)
#
# Within each tier, order is by created_at (first-come, first-served).

df_solo <- df_clean |>
  filter(solo) |>
  select(created_at, email) |>
  # Join with lindy eligibility to check if they're in
  left_join(lindy_eligible, by = "email") |>
  left_join(
    df_clean |> select(email, lindy) |> distinct(),
    by = "email"
  ) |>
  # Bring in previous Lindy status to determine queue tier
  left_join(
    if (nrow(prev_tally) > 0) {
      prev_tally |> select(email, prev_lindy_in)
    } else {
      tibble(email = character(), prev_lindy_in = logical())
    },
    by = "email"
  ) |>
  mutate(
    # Can participate in solo if:
    # - Not registered for lindy, OR
    # - Registered for lindy AND accepted
    can_queue_solo = !lindy | (lindy & coalesce(lindy_in, FALSE)),

    # Queue tier determines sort priority (see note above)
    solo_queue_tier = case_when(
      !coalesce(lindy, FALSE)          ~ 0L,  # Solo-only: eligible from registration
      coalesce(prev_lindy_in, FALSE)   ~ 1L,  # Already Lindy-confirmed last run
      TRUE                             ~ 2L   # Newly Lindy-confirmed this run
    )
  ) |>
  arrange(solo_queue_tier, created_at) |>
  mutate(
    # queue_position only counts people who *can* queue.
    # People blocked by Lindy waitlist should NOT consume a queue slot.
    queue_position = cumsum(can_queue_solo),
    solo_in = can_queue_solo & queue_position <= SOLO_QUOTA
  )

solo_summary <- df_solo |>
  summarise(
    total_registrations = n(),
    can_queue = sum(can_queue_solo),
    eligible = sum(solo_in, na.rm = TRUE),
    quota = SOLO_QUOTA
  )

cat("\n=== SOLO SUMMARY ===\n")
print(solo_summary)

cat("\n=== SOLO QUEUE BY TIER ===\n")
df_solo |>
  group_by(solo_queue_tier) |>
  summarise(
    description = case_when(
      first(solo_queue_tier) == 0L ~ "Solo-only registrants",
      first(solo_queue_tier) == 1L ~ "Previously Lindy-confirmed",
      TRUE                         ~ "Newly Lindy-confirmed this run"
    ),
    total = n(),
    can_queue = sum(can_queue_solo),
    solo_in = sum(solo_in, na.rm = TRUE),
    .groups = "drop"
  ) |>
  print()

solo_eligible <- df_solo |>
  select(email, solo_in)

# ── Monotonic safety net: never demote a previously confirmed solo participant ──
if (nrow(prev_tally) > 0) {
  solo_before <- solo_eligible  # snapshot before overlay
  solo_eligible <- solo_eligible |>
    left_join(prev_tally |> select(email, prev_solo_in), by = "email") |>
    mutate(solo_in = coalesce(solo_in, FALSE) | coalesce(prev_solo_in, FALSE)) |>
    select(email, solo_in)
  
  n_saved <- sum(solo_eligible$solo_in & !coalesce(solo_before$solo_in, FALSE))
  if (n_saved > 0) {
    cat("  ⚠ Monotonic safety net saved", n_saved, "solo participants from demotion\n")
  }
}
```

## Final Tally - Combine All Results

```{r}
#| label: final-tally

# Create on-hold indicator from lindy processing
lindy_on_hold_emails <- if (nrow(lindy_on_hold) > 0) {
  lindy_on_hold |> distinct(email) |> mutate(is_on_hold = TRUE)
} else {
  tibble(email = character(), is_on_hold = logical())
}

# Combine all eligibility results
final_tally <- df_clean |>
  select(
    id, created_at, email, name, pass, role, level,
    lindy, solo,
    has_partner, partner_email,
    payment_status, amount_cents
  ) |>
  left_join(lindy_eligible, by = "email") |>
  left_join(solo_eligible, by = "email") |>
  left_join(lindy_on_hold_emails, by = "email") |>
  mutate(
    # Determine overall status
    status = case_when(
      # On hold - waiting for partner to register within hold period
      coalesce(is_on_hold, FALSE) ~ "ON_HOLD",
      
      # All registered tracks are accepted
      (is.na(lindy) | !lindy | coalesce(lindy_in, FALSE)) &
      (is.na(solo) | !solo | coalesce(solo_in, FALSE)) &
      (coalesce(lindy_in, FALSE) | coalesce(solo_in, FALSE)) ~ "CONFIRMED",
      
      # At least one track accepted, others on waitlist
      coalesce(lindy_in, FALSE) | coalesce(solo_in, FALSE) ~ "PARTIAL",
      
      # No tracks accepted
      TRUE ~ "WAITLIST"
    )
  )

# Sanity check: final_tally must have exactly one row per email
dup_emails <- final_tally |> count(email) |> filter(n > 1)
if (nrow(dup_emails) > 0) {
  warning("DUPLICATE EMAILS in final_tally: ", paste(dup_emails$email, collapse = ", "))
}
stopifnot("final_tally has duplicate emails!" = nrow(dup_emails) == 0)

# Status summary
status_summary <- final_tally |>
  count(status) |>
  arrange(desc(n))

cat("\n=== FINAL STATUS SUMMARY ===\n")
print(status_summary)

# Detailed breakdown
cat("\n=== DETAILED BREAKDOWN ===\n")
final_tally |>
  group_by(status) |>
  summarise(
    count = n(),
    lindy_in = sum(lindy_in, na.rm = TRUE),
    solo_in = sum(solo_in, na.rm = TRUE),
    .groups = "drop"
  ) |>
  print()
```

## State Diff — Previous vs New

```{r}
#| label: state-diff

# Compare current results against previous run to identify transitions
# This is the key output when re-running: who changed status?

if (nrow(prev_tally) > 0) {
  state_diff <- final_tally |>
    select(email, name, role, level, status, lindy_in, solo_in) |>
    left_join(prev_tally, by = "email", suffix = c("", "_prev")) |>
    mutate(
      prev_status  = coalesce(prev_status, "NEW"),
      status_changed = status != prev_status,
      transition = if_else(
        status_changed,
        paste0(prev_status, " -> ", status),
        "no change"
      )
    )
  
  # ── People who improved (Waitlist/On Hold → Confirmed/Partial) ──
  promotions <- state_diff |>
    filter(
      status_changed,
      prev_status %in% c("WAITLIST", "ON_HOLD", "PARTIAL", "NEW"),
      status %in% c("CONFIRMED", "PARTIAL")
    ) |>
    select(name, email, role, level, transition)
  
  cat("\n=== PROMOTIONS (need confirmation email) ===\n")
  if (nrow(promotions) > 0) {
    print(promotions, n = 100)
  } else {
    cat("No promotions since last run.\n")
  }
  
  # ── People whose status worsened (should not happen with locking) ──
  demotions <- state_diff |>
    filter(
      status_changed,
      prev_status %in% c("CONFIRMED", "PARTIAL"),
      status %in% c("WAITLIST", "ON_HOLD")
    ) |>
    select(name, email, role, level, transition)
  
  if (nrow(demotions) > 0) {
    cat("\n⚠ WARNING: DEMOTIONS DETECTED (should not happen!) ===\n")
    print(demotions, n = 100)
  }
  
  # ── New registrations (not in previous run) ──
  new_regs <- state_diff |>
    filter(prev_status == "NEW") |>
    select(name, email, role, level, status)
  
  cat("\n=== NEW REGISTRATIONS SINCE LAST RUN ===\n")
  if (nrow(new_regs) > 0) {
    print(new_regs, n = 100)
  } else {
    cat("No new registrations.\n")
  }
  
  # ── Full transition summary ──
  cat("\n=== TRANSITION SUMMARY ===\n")
  state_diff |>
    count(transition) |>
    arrange(desc(n)) |>
    print()
  
} else {
  cat("First run — no previous state to compare against.\n")
}
```

## Write Lindy Levels to Google Sheets

```{r}
#| label: write-levels-to-sheets

# Join names and payment_status onto lindy_pairs for display
lindy_pairs_display <- lindy_pairs |>
  left_join(df_clean |> select(email, name, payment_status), by = c("email_leader" = "email")) |>
  rename(leader_name = name, payment_status_leader = payment_status) |>
  left_join(df_clean |> select(email, name, payment_status), by = c("email_follower" = "email")) |>
  rename(follower_name = name, payment_status_follower = payment_status) |>
  mutate(
    leader_paid = coalesce(str_to_lower(payment_status_leader) == "captured" | str_detect(str_to_lower(payment_status_leader), "paid"), FALSE),
    follower_paid = coalesce(str_to_lower(payment_status_follower) == "captured" | str_detect(str_to_lower(payment_status_follower), "paid"), FALSE)
  ) |>
  select(level, pair_number, leader_name, leader_email = email_leader, leader_paid,
         created_at_leader,
         follower_name, follower_email = email_follower, follower_paid,
         is_couple, eligible, created_at_follower) |>
  arrange(level, pair_number)

# Define sheet names per level
levels_to_write <- list(
  "Lindy Advanced"     = "advanced",
  "Lindy Int-Adv"      = "int-advanced",
  "Lindy Intermediate"  = "intermediate"
)

# Write each level to its own sheet with a summary header
for (sheet_name in names(levels_to_write)) {
  lvl <- levels_to_write[[sheet_name]]
  lvl_data <- lindy_pairs_display |> filter(level == lvl) |> select(-level)
  quota_val <- LINDY_QUOTAS |> filter(level == lvl) |> pull(quota)

  complete    <- sum(!is.na(lvl_data$leader_email) & !is.na(lvl_data$follower_email))
  no_leader   <- sum(is.na(lvl_data$leader_email) & !is.na(lvl_data$follower_email))
  no_follower <- sum(!is.na(lvl_data$leader_email) & is.na(lvl_data$follower_email))
  spots_left  <- max(0, quota_val - complete)

  # Summary block (written to rows 1-2)
  summary_df <- tibble(
    Metric = c("Quota", "Complete pairs", "Missing leaders", "Missing followers", "Spots left"),
    Value  = c(quota_val, complete, no_leader, no_follower, spots_left)
  )

  # Write summary first (creates/overwrites the sheet)
  write_sheet(summary_df, ss = GOOGLE_SHEETS$registrations_2026, sheet = sheet_name)
  # Append pairs table starting at row 4 (leaving a blank row separator)
  range_write(lvl_data, ss = GOOGLE_SHEETS$registrations_2026, sheet = sheet_name, range = "A4")

  cat("Written sheet:", sheet_name, "—", complete, "complete pairs,", spots_left, "spots left\n")
}
```

## Write Solo Jazz to Google Sheets

```{r}
#| label: write-solo-to-sheets

solo_display <- final_tally |>
  filter(coalesce(solo, FALSE)) |>
  left_join(
    df_solo |> select(email, solo_queue_tier, queue_position),
    by = "email"
  ) |>
  mutate(
    paid = coalesce(
      str_to_lower(payment_status) == "captured" |
        str_detect(str_to_lower(coalesce(payment_status, "")), "paid"),
      FALSE
    ),
    solo_status = if_else(coalesce(solo_in, FALSE), "Confirmed", "Waitlist"),
    queue_tier_label = case_when(
      solo_queue_tier == 0L ~ "Solo-only",
      solo_queue_tier == 1L ~ "Prev. Lindy-confirmed",
      TRUE                  ~ "Newly Lindy-confirmed"
    )
  ) |>
  arrange(solo_status, queue_position) |>
  select(
    solo_status, queue_position,
    name, email, role, level,
    paid, created_at,
    queue_tier_label
  )

confirmed_count <- sum(coalesce(solo_display$solo_status == "Confirmed", FALSE))
waitlist_count  <- sum(coalesce(solo_display$solo_status == "Waitlist",  FALSE))
spots_left      <- max(0L, SOLO_QUOTA - confirmed_count)

solo_summary_df <- tibble(
  Metric = c("Quota", "Confirmed", "Waitlist", "Spots left"),
  Value  = c(SOLO_QUOTA, confirmed_count, waitlist_count, spots_left)
)

write_sheet(solo_summary_df, ss = GOOGLE_SHEETS$registrations_2026, sheet = "Solo Jazz")
range_write(
  solo_display,
  ss    = GOOGLE_SHEETS$registrations_2026,
  sheet = "Solo Jazz",
  range = "A4"
)

cat("Written sheet: Solo Jazz —", confirmed_count, "confirmed,",
    waitlist_count, "waitlisted,", spots_left, "spots left\n")
```

## Waitlist Details

```{r}
#| label: waitlist-details

# Show people on waitlist with reasons
waitlist <- final_tally |>
  filter(status %in% c("WAITLIST", "PARTIAL")) |>
  mutate(
    waitlist_for = case_when(
      lindy & !coalesce(lindy_in, FALSE) & solo & !coalesce(solo_in, FALSE) ~ "Lindy + Solo",
      lindy & !coalesce(lindy_in, FALSE) ~ "Lindy",
      solo & !coalesce(solo_in, FALSE) ~ "Solo",
      TRUE ~ "Unknown"
    )
  ) |>
  select(name, email, status, waitlist_for, level, role, has_partner, partner_email)

# Show on-hold registrations (waiting for partner within hold period)
on_hold <- final_tally |>
  filter(status == "ON_HOLD") |>
  select(name, email, level, role, partner_email, created_at) |>
  mutate(
    hold_expires = created_at + as.difftime(PARTNER_HOLD_DAYS, units = "days")
  )

cat("\n=== ON HOLD (partner has", PARTNER_HOLD_DAYS, "days to register) ===\n")
if (nrow(on_hold) > 0) {
  print(on_hold, n = 50)
} else {
  cat("No registrations currently on hold.\n")
}

cat("\n=== WAITLIST DETAILS ===\n")
print(waitlist, n = 50)
```

## Persist Final Tally (source of truth for next run)

```{r}
#| label: persist-final-tally

# Write the final_tally to Google Sheets so the NEXT run can use it as
# "previous state" for the state-diff and for locking in confirmed results.
write_sheet(final_tally, ss = GOOGLE_SHEETS$registrations_2026, sheet = "final_tally")
cat("Final tally written to Google Sheets (", nrow(final_tally), "rows)\n")
cat("Run completed at:", format(RUN_TIMESTAMP, "%Y-%m-%d %H:%M:%S %Z"), "\n")
```

## Update Firebase with Results (Optional)

```{r}
#| label: update-firebase
#| eval: false

# Only update Firebase for registrations whose status, lindy_in, or solo_in
# have changed since the last run (or are brand-new registrations).

changed <- final_tally |>
  select(id, email, status, lindy_in, solo_in) |>
  left_join(prev_tally, by = "email") |>
  mutate(
    prev_status   = coalesce(prev_status, "NEW"),
    prev_lindy_in = coalesce(prev_lindy_in, FALSE),
    prev_solo_in  = coalesce(prev_solo_in, FALSE),
    cur_lindy_in  = coalesce(lindy_in, FALSE),
    cur_solo_in   = coalesce(solo_in, FALSE)
  ) |>
  filter(
    status       != prev_status |
    cur_lindy_in != prev_lindy_in |
    cur_solo_in  != prev_solo_in
  )

cat("Registrations to update:", nrow(changed), "of", nrow(final_tally), "total\n\n")

if (nrow(changed) == 0) {
  cat("Nothing to update — Firebase is already in sync.\n")
} else {
  for (i in seq_len(nrow(changed))) {
    reg <- changed[i, ]

    fn_update_registration(
      doc_id = reg$id,
      fields = list(
        lindy_in = reg$cur_lindy_in,
        solo_in  = reg$cur_solo_in,
        status   = reg$status
      )
    )

    cat("Updated:", reg$email, "—", reg$prev_status, "->", reg$status,
        " | lindy_in:", reg$cur_lindy_in, "| solo_in:", reg$cur_solo_in, "\n")
    Sys.sleep(0.5)  # Rate limiting
  }

  cat("\nFirebase update complete!", nrow(changed), "registrations updated.\n")
}
```
