---
title: "MSS 2026 - Confirmation Emails & Payment Capture"
format: html
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false

rm(list = ls())

source(here::here("R", "config.R"))
source(here::here("R", "helpers.R"))
source(here::here("R", "firestore_api.R"))
fn_setup()
```

## Load Registration Results

The source of truth for who is CONFIRMED / PARTIAL / WAITLIST comes from the
registration processing step (`01_registration/2026_registration_lindy.qmd`),
which writes the `final_tally` sheet to Google Sheets.

Payment details (Stripe PaymentIntent IDs, payment method) come from Firebase.

```{r}
#| label: load-data

# ── 1. Read final_tally from the registration step (status, eligibility) ──
final_tally <- read_sheet(
  GOOGLE_SHEETS$registrations_2026,
  sheet = "final_tally"
)

cat("Loaded final_tally:", nrow(final_tally), "rows\n")
final_tally |> count(status) |> print()

# ── 2. Fetch payment & email-tracking details from Firebase ──
df_firebase <- fn_get_registrations() |>
  filter(!is.na(email) & email != "") |>
  mutate(email = str_to_lower(email))

# Ensure expected columns exist (some may be absent if never written)
if (!"stripe_payment_intent_id" %in% names(df_firebase)) {
  df_firebase$stripe_payment_intent_id <- NA_character_
}
if (!"payment_method" %in% names(df_firebase)) {
  df_firebase$payment_method <- NA_character_
}
if (!"confirmation_email_sent" %in% names(df_firebase)) {
  df_firebase$confirmation_email_sent <- FALSE
}
if (!"confirmation_email_status" %in% names(df_firebase)) {
  df_firebase$confirmation_email_status <- NA_character_
}
if (!"payment_status" %in% names(df_firebase)) {
  df_firebase$payment_status <- NA_character_
}
if (!"fan" %in% names(df_firebase)) {
  df_firebase$fan <- FALSE
}
if (!"stripe_customer_id" %in% names(df_firebase)) {
  df_firebase$stripe_customer_id <- NA_character_
}
if (!"stripe_payment_method_id" %in% names(df_firebase)) {
  df_firebase$stripe_payment_method_id <- NA_character_
}

df_firebase_slim <- df_firebase |>
  select(id, stripe_payment_intent_id, stripe_customer_id,
         stripe_payment_method_id, payment_method,
         confirmation_email_sent, confirmation_email_status, payment_status, fan)

# ── 3. Join status with payment details ──
# Drop payment_status from final_tally before joining — Firebase is the
# up-to-date source and df_firebase_slim already carries it.
df_registrations <- final_tally |>
  select(-any_of("payment_status")) |>
  left_join(df_firebase_slim, by = "id") |>
  mutate(
    name = str_to_title(name),

    # Infer payment method when not explicitly set
    payment_method = case_when(
      !is.na(payment_method) & payment_method != "" ~ payment_method,
      !is.na(stripe_payment_intent_id) &
        stripe_payment_intent_id != ""              ~ "card",
      TRUE                                          ~ "epassi"
    ),

    # Human-readable summaries
    registered_for = pmap_chr(list(lindy, solo), function(l, s) {
      parts <- c(
        if (coalesce(l, FALSE)) "Lindy" else NULL,
        if (coalesce(s, FALSE)) "Solo"  else NULL
      )
      if (length(parts) == 0) "-" else paste(parts, collapse = " + ")
    }),
    confirmed_for = pmap_chr(list(lindy_in, solo_in), function(l, s) {
      parts <- c(
        if (coalesce(l, FALSE)) "Lindy" else NULL,
        if (coalesce(s, FALSE)) "Solo"  else NULL
      )
      if (length(parts) == 0) "-" else paste(parts, collapse = " + ")
    }),

    # Payment-method surcharge — needs to be added when the price is
    # recalculated (fn_calculate_price doesn't include it).
    # When total_price comes from amount_cents it already contains the surcharge.
    #   ePassi / Smartum / Edenred: +5€
    #   Invoice:                    +10€
    #   Card:                        0€
    payment_surcharge = case_when(
      payment_method == "epassi"  ~ 5,
      payment_method == "invoice" ~ 10,
      TRUE ~ 0
    ),

    # Price: use the pre-authorized amount from Firebase (it includes pass + fan + surcharge).
    # Exception: PARTIAL confirmations — recalculate based on confirmed tracks
    # only, since the user won't pay for the track they didn't get into.
    # WAITLIST people do not pay for anything (fan included) — price is 0.
    # Fallback: if amount_cents is NA (e.g. non-card payments), recalculate.
    # In both recalculated cases, payment_surcharge is added (0 for card).
    total_price = case_when(
      status == "WAITLIST" ~ 0,
      status == "PARTIAL" ~ pmap_dbl(list(lindy_in, solo_in, fan), function(l, s, f) {
        fn_calculate_price(
          lindy_in = coalesce(l, FALSE),
          solo_in  = coalesce(s, FALSE),
          fan      = coalesce(as.logical(f), FALSE)
        )
      }) + payment_surcharge,
      !is.na(amount_cents) ~ amount_cents / 100,
      TRUE ~ pmap_dbl(list(lindy_in, solo_in, fan), function(l, s, f) {
        fn_calculate_price(
          lindy_in = coalesce(l, FALSE),
          solo_in  = coalesce(s, FALSE),
          fan      = coalesce(as.logical(f), FALSE)
        )
      }) + payment_surcharge
    )
  )

# ── 4. Compute per-level, per-role sold-out flag from the locked pairs sheet ──
# Two distinct conditions per level:
#   * leader_spots_left  > 0  → still recruiting leaders → follower waitlist gets
#     the "we don't have enough leaders" message ("waitlist", with options).
#   * leader_spots_left == 0  → leader quota filled. If a follower is still on
#     the waitlist she can't be helped by inviting a leader (the level is full
#     for followers too, since she's beyond the overflow), so use "sold_out".
#   * For leaders on waitlist: leaders only end up on the waitlist when leader
#     quota is filled, so always use "sold_out" for them.
#
# Lindy levels only; Solo waitlist always gets the sold-out message since the
# "find a leader" advice never applies there.
lindy_pairs_locked <- tryCatch(
  read_sheet(GOOGLE_SHEETS$registrations_2026, sheet = "lindy_pairs_locked"),
  error = function(e) {
    warning("Could not load lindy_pairs_locked sheet — defaulting all levels to sold_out = FALSE")
    NULL
  }
)

level_capacity <- if (!is.null(lindy_pairs_locked) && nrow(lindy_pairs_locked) > 0) {
  # New schema (preferred): leader_eligible / follower_eligible columns.
  # Old schema fallback: derive from complete-pair count vs quota.
  has_role_cols <- all(c("leader_eligible", "follower_eligible") %in%
                       names(lindy_pairs_locked))

  if (has_role_cols) {
    lindy_pairs_locked |>
      group_by(level) |>
      summarise(
        confirmed_leaders   = sum(coalesce(as.logical(leader_eligible),   FALSE)),
        confirmed_followers = sum(coalesce(as.logical(follower_eligible), FALSE)),
        quota               = first(quota),
        .groups = "drop"
      ) |>
      mutate(
        leader_spots_left = pmax(0L, quota - confirmed_leaders),
        # Leader quota filled → any follower still waitlisted is beyond overflow
        # → "level is full for her too".
        lindy_level_sold_out = leader_spots_left == 0L
      )
  } else {
    lindy_pairs_locked |>
      group_by(level) |>
      summarise(
        complete_pairs = sum(!is.na(email_leader) & !is.na(email_follower), na.rm = TRUE),
        quota          = first(quota),
        .groups = "drop"
      ) |>
      mutate(
        leader_spots_left    = pmax(0L, quota - complete_pairs),
        lindy_level_sold_out = leader_spots_left == 0L
      )
  }
} else {
  tibble(level = character(), leader_spots_left = integer(), lindy_level_sold_out = logical())
}

cat("\nLindy level capacity:\n")
print(level_capacity)

# Join sold-out flag onto registrations (by their Lindy level)
df_registrations <- df_registrations |>
  left_join(level_capacity |> select(level, lindy_level_sold_out), by = "level") |>
  mutate(
    # A WAITLIST person is "sold out" when:
    #   - Solo-only on waitlist (no leader logic applies), OR
    #   - They are a leader on waitlist (leader quota necessarily full), OR
    #   - Their Lindy level's leader-quota is filled (so they're a follower
    #     beyond the overflow, can't be helped by a new leader)
    is_sold_out = case_when(
      status != "WAITLIST" ~ FALSE,
      !coalesce(lindy, FALSE) ~ TRUE,
      role == "leader" ~ TRUE,
      TRUE ~ coalesce(lindy_level_sold_out, FALSE)
    )
  )

# Sanity check: must have exactly one row per email (no duplicates from join)
stopifnot(
  "df_registrations has duplicate emails after join!" =
    n_distinct(df_registrations$email) == nrow(df_registrations)
)

cat("\nRegistrations with payment details loaded:", nrow(df_registrations), "rows\n")
```

## Filter Registrations to Process

```{r}
#| label: filter-to-process

# Only process registrations that:
#   1. Have a final status of CONFIRMED, PARTIAL, or WAITLIST (skip ON_HOLD)
#   2. Have NOT already received an email for their CURRENT status
#      (allows re-processing when status changes, e.g. WAITLIST → CONFIRMED)
df_to_process <- df_registrations |>
  filter(status %in% c("CONFIRMED", "PARTIAL", "WAITLIST"),
         coalesce(confirmation_email_status, "new") != "CONFIRMED") |>
  filter(
    !coalesce(as.logical(confirmation_email_sent), FALSE) |
    coalesce(confirmation_email_status, "") != status
  )

# Separate new registrations from status-changed ones (for diagnostics)
df_new <- df_to_process |>
  filter(!coalesce(as.logical(confirmation_email_sent), FALSE))
df_status_changed <- df_to_process |>
  filter(coalesce(as.logical(confirmation_email_sent), FALSE))

cat("\n=== REGISTRATIONS TO PROCESS ===\n")
cat("Total:", nrow(df_to_process), "\n")
cat("  New (never emailed):", nrow(df_new), "\n")
cat("  Status changed (re-process):", nrow(df_status_changed), "\n")

if (nrow(df_status_changed) > 0) {
  cat("\n  Status changes:\n")
  df_status_changed |>
    mutate(transition = paste(coalesce(confirmation_email_status, "?"), "→", status)) |>
    count(transition) |>
    print()
}

cat("\nBy status:\n")
df_to_process |> count(status) |> print()

cat("\nBy payment method:\n")
df_to_process |> count(payment_method) |> print()

cat("\nBy status × payment method:\n")
df_to_process |> count(status, payment_method) |> print()
```

## Email Templates

```{r}
#| label: email-templates

# Logo for email footer
img_string <- fn_get_logo()

# Payment text blocks (all from shared config / helpers)
# Note: ePassi text is generated per-user (needs total_price for surcharge)
txt_payment_card_ok     <- EMAIL_MESSAGES$payment_captured
txt_payment_card_failed <- fn_payment_card_failed_text()

# ─────────────────────────────────────────────────────
# Build email
# ─────────────────────────────────────────────────────

fn_build_email <- function(name, status, role, level,
                           registered_for, confirmed_for,
                           total_price, fan, payment_section,
                           is_sold_out = FALSE) {

  # Guard against NULL / NA in every input
  safe_chr <- function(x, default = "") if (is.null(x) || length(x) == 0) default else coalesce(as.character(x), default)
  safe_num <- function(x, default = 0)  if (is.null(x) || length(x) == 0) default else coalesce(as.numeric(x), default)
  safe_lgl <- function(x, default = FALSE) if (is.null(x) || length(x) == 0) default else coalesce(as.logical(x), default)

  name            <- safe_chr(name)
  status          <- safe_chr(status, "WAITLIST")
  role            <- str_to_title(safe_chr(role, "-"))
  level           <- str_to_title(safe_chr(level, "-"))
  registered_for  <- safe_chr(registered_for, "-")
  confirmed_for   <- safe_chr(confirmed_for, "-")
  total_price     <- safe_num(total_price)
  fan             <- safe_lgl(fan)
  payment_section <- safe_chr(payment_section)
  is_sold_out     <- safe_lgl(is_sold_out)

  # Intro text (from shared config)
  intro_text <- case_when(
    status == "CONFIRMED" ~ EMAIL_MESSAGES$confirmation,
    status == "PARTIAL"   ~ EMAIL_MESSAGES$partial_confirmation,
    is_sold_out           ~ EMAIL_MESSAGES$waitlist_sold_out,
    TRUE                  ~ EMAIL_MESSAGES$waitlist
  )

  # Fan line (only if they ordered one)
  fan_line <- if (fan) "\n  - Fan: **Yes**" else ""

  # Registration details
  # Note: WAITLIST people do not pay for the fan (18€), so we don't show it
  details_text <- if (status == "WAITLIST") {
    glue(
      "These are the details of your registration:\n",
      "  - You registered for: **{registered_for}**\n",
      "  - Role: **{role}**\n",
      "  - Level: **{level}**"
    )
  } else {
    glue(
      "These are the details of your registration:\n",
      "  - You registered for: **{registered_for}**\n",
      "  - Role: **{role}**\n",
      "  - Level: **{level}**\n",
      "  - You have been confirmed for: **{confirmed_for}**",
      fan_line, "\n",
      "  - Total price: **{total_price}€**"
    )
  }

  # Waitlist options (WAITLIST only — PARTIAL people are confirmed for Lindy
  # but waitlisted for Solo Jazz, which has no partner requirement,
  # so the "find a leader" suggestions don't apply).
  # When the level is fully sold out, skip the leader-shortage advice and
  # show a simpler "we'll contact you" message instead.
  waitlist_text <- if (status == "WAITLIST") {
    if (is_sold_out) EMAIL_MESSAGES$waitlist_options_sold_out else fn_waitlist_options()
  } else {
    NULL
  }

  # Social links (from shared config)
  social_text <- fn_social_links()

  # Closing text (softer wording for waitlisted users)
  closing_text <- if (status == "WAITLIST") "We'll keep you updated!" else "See you soon in Helsinki!"

  # Build body from non-empty sections (avoids blank-line gaps)
  sections <- c(
    glue("Hello {name}"),
    intro_text,
    details_text,
    if (nzchar(payment_section)) payment_section else NULL,
    waitlist_text,
    social_text,
    closing_text,
    img_string
  )

  email_body <- md(paste(sections, collapse = "\n\n"))

  compose_email(
    body = email_body,
    title = "Welcome to Midnight Sun Swing",
    footer = "Midnight Sun Swing"
  )
}

# ─────────────────────────────────────────────────────
# Email subject helper
# ─────────────────────────────────────────────────────

fn_get_subject <- function(status) {
  case_when(
    status == "CONFIRMED" ~ EMAIL_SUBJECTS$confirmation,
    status == "PARTIAL"   ~ EMAIL_SUBJECTS$partial_confirmation,
    status == "WAITLIST"  ~ EMAIL_SUBJECTS$waitlist,
    TRUE ~ paste0("MSS ", CURRENT_YEAR, " - Registration Update")
  )
}
```

## Preview Emails (Dry Run — All Possible Cases)

```{r}
#| label: preview-emails

# ─────────────────────────────────────────────────────────────────────
# Dry-run preview: one email for EVERY possible case in the flow.
# Cases are defined by: status × payment_method × capture_outcome.
# This ensures you review every email variant before sending anything.
# ─────────────────────────────────────────────────────────────────────

email_cases <- tribble(
  ~case_id, ~case_label,                        ~status,     ~payment_method, ~capture_outcome, ~registered_for, ~confirmed_for, ~lindy_in, ~solo_in, ~is_sold_out,
   1L, "CONFIRMED + Card (captured)",            "CONFIRMED", "card",    "ok",             "Lindy + Solo", "Lindy + Solo", TRUE,  TRUE,  FALSE,
   2L, "CONFIRMED + Card (capture failed)",      "CONFIRMED", "card",    "failed",         "Lindy + Solo", "Lindy + Solo", TRUE,  TRUE,  FALSE,
   3L, "CONFIRMED + ePassi",                     "CONFIRMED", "epassi",  NA_character_,    "Lindy + Solo", "Lindy + Solo", TRUE,  TRUE,  FALSE,
   4L, "CONFIRMED + Invoice",                    "CONFIRMED", "invoice", NA_character_,    "Lindy + Solo", "Lindy + Solo", TRUE,  TRUE,  FALSE,
   5L, "PARTIAL + Card (captured)",              "PARTIAL",   "card",    "ok",             "Lindy + Solo", "Lindy",        TRUE,  FALSE, FALSE,
   6L, "PARTIAL + Card (capture failed)",        "PARTIAL",   "card",    "failed",         "Lindy + Solo", "Lindy",        TRUE,  FALSE, FALSE,
   7L, "PARTIAL + ePassi",                       "PARTIAL",   "epassi",  NA_character_,    "Lindy + Solo", "Lindy",        TRUE,  FALSE, FALSE,
   8L, "PARTIAL + Invoice",                      "PARTIAL",   "invoice", NA_character_,    "Lindy + Solo", "Lindy",        TRUE,  FALSE, FALSE,
   9L, "WAITLIST (leader shortage)",             "WAITLIST",  NA_character_, NA_character_, "Lindy",        "-",            FALSE, FALSE, FALSE,
  10L, "WAITLIST (level fully sold out)",        "WAITLIST",  NA_character_, NA_character_, "Lindy",        "-",            FALSE, FALSE, TRUE
)

# Use a real registration as template for name / role / level / fan
template <- if (nrow(df_to_process) > 0) {
  df_to_process |> slice(1)
} else {
  df_registrations |> slice(1)
}

cat("Using template registration:", template$name, "(", template$email, ")\n")
cat("Generating", nrow(email_cases), "preview emails...\n")

for (idx in seq_len(nrow(email_cases))) {
  case <- email_cases[idx, ]

  # Calculate price for this specific case (add payment-method surcharge)
  # WAITLIST people do not pay for the fan
  case_fan <- if (case$status == "WAITLIST") FALSE else coalesce(as.logical(template$fan), FALSE)
  mock_price <- fn_calculate_price(
    lindy_in = case$lindy_in,
    solo_in  = case$solo_in,
    fan      = case_fan
  )
  if (!is.na(case$payment_method)) {
    if (case$payment_method == "epassi")  mock_price <- mock_price + 5
    if (case$payment_method == "invoice") mock_price <- mock_price + 10
  }

  # Determine the payment section for this case
  payment_section <- if (case$status %in% c("CONFIRMED", "PARTIAL")) {
    if (!is.na(case$payment_method) && case$payment_method == "card") {
      if (!is.na(case$capture_outcome) && case$capture_outcome == "ok") {
        txt_payment_card_ok
      } else {
        txt_payment_card_failed
      }
    } else if (!is.na(case$payment_method) && case$payment_method == "invoice") {
      fn_payment_invoice_text()
    } else {
      # ePassi: surcharge is always included in mock_price / total_price
      fn_payment_epassi_text(mock_price, surcharge_included = TRUE)
    }
  } else {
    ""
  }

  cat("\n", strrep("=", 70), "\n", sep = "")
  cat(" CASE ", case$case_id, "/", nrow(email_cases), ": ", case$case_label, "\n", sep = "")
  cat(strrep("=", 70), "\n")
  cat("  To:              ", template$email, "\n")
  cat("  Name:            ", template$name, "\n")
  cat("  Subject:         ", fn_get_subject(case$status), "\n")
  cat("  Status:          ", case$status, "\n")
  cat("  Payment method:  ", coalesce(case$payment_method, "(n/a)"), "\n")
  if (!is.na(case$capture_outcome)) {
    cat("  Capture outcome: ", case$capture_outcome, "\n")
  }
  cat("  Registered for:  ", case$registered_for, "\n")
  cat("  Confirmed for:   ", case$confirmed_for, "\n")
  cat("  Price:           ", mock_price, "€\n")
  cat(strrep("-", 70), "\n")

  preview_email <- fn_build_email(
    name            = template$name,
    status          = case$status,
    role            = template$role,
    level           = template$level,
    registered_for  = case$registered_for,
    confirmed_for   = case$confirmed_for,
    total_price     = mock_price,
    fan             = case_fan,
    payment_section = payment_section,
    is_sold_out     = case$is_sold_out
  )

  print(preview_email)
}
```

## Process Confirmations (Capture Payments + Send Emails)

```{r}
#| label: process-confirmations
#| eval: false

# ⚠️ SET eval: true TO ACTUALLY PROCESS
# This will capture payments and send emails!
#
# FAIL-FAST: The loop STOPS on any error — no silent failures.
# Already-processed registrations are automatically skipped (idempotent),
# so it is always safe to fix the issue and re-run from the top.
#
# Stripe capture failures are recorded in Firebase as 'capture_failed'.
# On re-run, those registrations get the card-failed email instead of
# re-attempting the capture — review and reset payment_status if you
# want to retry the capture.

results <- list(
  processed        = 0L,
  payment_captured = 0L,
  payment_skipped  = 0L,
  epassi_pending   = 0L,
  invoice_pending  = 0L,
  emails_sent      = 0L
)

for (i in 1:nrow(df_to_process)) {
  reg <- df_to_process[i, ]

  cat("\n", strrep("=", 60), "\n", sep = "")
  cat(" Processing ", i, "/", nrow(df_to_process), ": ", reg$email, "\n", sep = "")
  cat(strrep("=", 60), "\n")
  cat("  Status:          ", reg$status, "\n")
  cat("  Payment method:  ", reg$payment_method, "\n")
  cat("  Payment status:  ", coalesce(reg$payment_status, "(none)"), "\n")

  payment_section   <- ""
  already_captured  <- coalesce(reg$payment_status, "") == "captured"
  prev_capture_fail <- coalesce(reg$payment_status, "") %in% c("capture_failed", "pending",
                                                               "payment_failed", "canceled")

  # ── CONFIRMED / PARTIAL: handle payment ──────────────────────────
  if (reg$status %in% c("CONFIRMED", "PARTIAL")) {

    if (reg$payment_method == "card" &&
        !is.na(reg$stripe_payment_intent_id) &&
        reg$stripe_payment_intent_id != "") {

      if (already_captured) {
        # Already captured on a previous run — nothing to do
        cat("  ⏭ Payment already captured — skipping Stripe call\n")
        results$payment_skipped <- results$payment_skipped + 1L
        payment_section <- txt_payment_card_ok

      } else if (prev_capture_fail) {
        # A previous run tried to capture and failed (likely expired pre-auth).
        # Try off-session charge using the stored card before falling back
        # to bank transfer instructions.
        has_card_on_file <- !is.na(reg$stripe_customer_id) &&
          reg$stripe_customer_id != "" &&
          !is.na(reg$stripe_payment_method_id) &&
          reg$stripe_payment_method_id != ""

        off_session_ok <- FALSE
        if (has_card_on_file) {
          cat("  Attempting off-session charge with stored card...\n")
          charge_amount <- reg$total_price * 100
          stmt_suffix <- case_when(
            coalesce(reg$solo_in, FALSE) ~ "Lindy + Solo Pass",
            TRUE                         ~ "Lindy Pass"
          )
          off_session_ok <- tryCatch({
            fn_create_off_session_payment(
              customer_id       = reg$stripe_customer_id,
              payment_method_id = reg$stripe_payment_method_id,
              amount_cents      = charge_amount,
              description       = glue("MSSF 2026 - {reg$name}"),
              statement_descriptor_suffix = stmt_suffix
            )
            TRUE
          }, error = function(e) {
            cat("  ⚠ Off-session charge failed: ", conditionMessage(e), "\n")
            FALSE
          })
        }

        if (off_session_ok) {
          fn_update_registration(reg$id, list(payment_status = "captured"))
          results$payment_captured <- results$payment_captured + 1L
          cat("  ✓ Payment captured via off-session charge\n")
          payment_section <- txt_payment_card_ok
        } else {
          cat("  Falling back to card-failed instructions (bank transfer)\n")
          payment_section <- txt_payment_card_failed
        }

      } else {
        # First attempt — capture the pre-authorized Stripe payment.
        # For PARTIAL, capture only the recalculated (lower) amount.
        capture_amount <- if (reg$status == "PARTIAL") reg$total_price * 100 else NULL
        cat("  Capturing payment: ", reg$stripe_payment_intent_id, "\n")

        capture_ok <- tryCatch({
          fn_capture_payment(reg$stripe_payment_intent_id, amount_to_capture = capture_amount)
          TRUE
        }, error = function(e) {
          # Record failure in Firebase so the next re-run won't retry blindly
          fn_update_registration(reg$id, list(
            payment_status = "capture_failed",
            capture_error  = conditionMessage(e)
          ))
          # Stop the loop with the original error visible
          stop(
            "Stripe capture FAILED for ", reg$email, ": ", conditionMessage(e), "\n",
            "  Firebase marked as 'capture_failed'.\n",
            "  Review the issue, then re-run. On re-run this registration will get\n",
            "  the card-failed email with alternative payment instructions.\n",
            "  To retry the capture, reset payment_status in Firebase first."
          )
        })

        fn_update_registration(reg$id, list(payment_status = "captured"))
        results$payment_captured <- results$payment_captured + 1L
        cat("  ✓ Payment captured\n")
        payment_section <- txt_payment_card_ok
      }

    } else if (reg$payment_method == "invoice") {
      cat("  Invoice payment — will send invoice separately\n")
      if (!already_captured) {
        fn_update_registration(reg$id, list(payment_status = "awaiting_invoice"))
      }
      results$invoice_pending <- results$invoice_pending + 1L
      payment_section <- fn_payment_invoice_text()

    } else {
      # ePassi / Smartum / bank transfer
      cat("  Non-card payment — sending payment instructions\n")
      if (!already_captured) {
        fn_update_registration(reg$id, list(payment_status = "awaiting_payment"))
      }
      results$epassi_pending <- results$epassi_pending + 1L
      # ePassi surcharge is always included in total_price
      payment_section <- fn_payment_epassi_text(
        reg$total_price,
        surcharge_included = TRUE
      )
    }

  # ── WAITLIST: keep pre-auth on hold ──────────────────────────────
  } else if (reg$status == "WAITLIST") {
    cat("  Waitlisted — keeping pre-auth on hold\n")
  }

  # ── Build and send email ─────────────────────────────────────────
  email <- fn_build_email(
    name            = reg$name,
    status          = reg$status,
    role            = reg$role,
    level           = reg$level,
    registered_for  = reg$registered_for,
    confirmed_for   = reg$confirmed_for,
    total_price     = reg$total_price,
    fan             = reg$fan,
    payment_section = payment_section,
    is_sold_out     = coalesce(reg$is_sold_out, FALSE)
  )
  
  email

  sent <- fn_send_email(
    email_object = email,
    to           = reg$email,
    subject      = fn_get_subject(reg$status)
  )

  if (!sent) {
    stop(
      "FAILED to send email to ", reg$email,
      " (registration ", i, "/", nrow(df_to_process), ").\n",
      "Fix the issue and re-run — already-processed registrations will be skipped."
    )
  }
  results$emails_sent <- results$emails_sent + 1L

  # ── Update Firebase (stops on failure to prevent duplicate emails) ──
  fn_update_registration(reg$id, list(
    confirmation_email_sent   = TRUE,
    confirmation_email_status = reg$status,
    confirmation_email_date   = format(Sys.time(), "%Y-%m-%dT%H:%M:%SZ")
  ))

  results$processed <- results$processed + 1L
  cat("  ✓ Done (", i, "/", nrow(df_to_process), ")\n", sep = "")

  # Pace the loop — gives time to inspect output and Ctrl-C if needed
  if (i < nrow(df_to_process)) {
    cat("  Waiting 3 seconds before next...\n")
    Sys.sleep(3)
  }
}

cat("\n\n", strrep("=", 60), "\n", sep = "")
cat(" PROCESSING COMPLETE\n")
cat(strrep("=", 60), "\n")
cat("Total processed:            ", results$processed, "\n")
cat("Card payments captured:     ", results$payment_captured, "\n")
cat("Card payments skipped (dup):", results$payment_skipped, "\n")
cat("ePassi/other pending:       ", results$epassi_pending, "\n")
cat("Invoice pending:            ", results$invoice_pending, "\n")
cat("Emails sent:                ", results$emails_sent, "\n")
```

## Summary Report

```{r}
#| label: summary


cat("=== REGISTRATION STATUS SUMMARY ===\n")
df_registrations |>
  count(status) |>
  arrange(desc(n)) |>
  print()

cat("\n=== CONFIRMATION EMAIL STATUS ===\n")
df_registrations |>
  mutate(
    email_sent    = coalesce(as.logical(confirmation_email_sent), FALSE),
    emailed_as    = coalesce(confirmation_email_status, "(none)"),
    status_changed = email_sent & emailed_as != status
  ) |>
  count(status, email_sent, emailed_as, status_changed) |>
  arrange(status) |>
  print()

cat("\n=== PAYMENT METHOD BREAKDOWN ===\n")
df_registrations |>
  filter(status %in% c("CONFIRMED", "PARTIAL")) |>
  count(payment_method, payment_status) |>
  pivot_wider(names_from = payment_method, values_from = n)
```
